This page and the next page should be removed

### 2021-01-18 analysis/manuscript.Rmd
update experiment 3 to new python functions

# Do you want to run the analysis for Experiment 3?
run_exp3 <- FALSE

@@

```{r exp3-preparation, eval=run_exp3}
# Read behavioral data for Experiment 3
data_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)

# Check average number of stimuli per condition
(objects_exp3 <- map(data_exp3, function(x) {
  x %<>% filter(part != "IV")
  table(x$condition) / 3
}) %>% bind_rows() %>% colMeans())
```

```{python exp3-preprocessing, eval=run_exp3}
# List raw EEG filenames
fnames_exp3 = sorted(glob.glob("data/exp3/EEG/*.vhdr"))

# Import behavioral data from R
metadata_exp3 = r.data_exp3

# Update stimulus triggers
preproc_params["event_id"] = {
    "match/upright": 241,
    "match/inverted": 242,
    "mismatch/upright": 243,
    "mismatch/inverted": 244,
}

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists("analysis/export/exp3-epo.fif"):
    # Read preprocessed data from file
    epochs_exp3 = mne.read_epochs("analysis/export/exp3-epo.fif", preload=True)
else:
    # Preprocess EEG data for Experiment 3
    epochs_exp3 = [
        preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
        for fname, meta in zip(fnames_exp3, metadata_exp3)
    ]
    # Combine epochs into a single data set
    epochs_exp3 = mne.concatenate_epochs(epochs_exp3)
    # Backup epochs and evokeds to the export folder
    epochs_exp3.save("analysis/export/exp3-epo.fif")
```

```{r exp3-analysis, eval=run_exp3}
# Re-import behavioral data and re-factorize some columns
data_exp3 <- py$epochs_exp3$metadata %>% mutate(
  part = factor(part, levels = c("I", "II", "III", "IV")),
  position = factor(position, levels = c("Inverted", "Upright")),
  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
  participant = factor(participant), item = factor(item)
)

# Check if ERPs were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp3-erps.RDS")) {
  # Read ERPs from file
  data_exp3 <- readRDS("analysis/export/exp3-erps.RDS")
} else {
  # Compute single-trial ERPs for Experiment 3
  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp3$get_data(), els = els) %>%
    set_names(comps$name) %>%
    cbind(data_exp3, .) %T>%
    saveRDS("analysis/export/exp3-erps.RDS")
}

# Remove the epochs to free up memory
py_run_string("del epochs_exp3")
import("gc")$collect()

# Remove any trials from part IV
data_exp3 %<>% filter(part != "IV") %>% droplevels()

# Check number of rejected epochs
rejected_exp3 <- data_exp3 %>% group_by(participant) %>% tally() %>% mutate(n = 672 - n) %>% pull(n)
mean(rejected_exp3)    # Mean
median(rejected_exp3)  # Median
range(rejected_exp3)   # Range

# Remove any trials excluded from conditions
data_exp3 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()

# Contrast coding for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
contrasts(data_exp3$position) <- MASS::ginv(contrasts_position)
contrasts(data_exp3$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp3$part) <- MASS::ginv(contrasts_part)

# New formula for LMMs
form_exp3 <- buildmer::tabulate.formula(
  ~ part * condition * position + (part * condition * position | participant) + (part * condition * position | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))

# New follow-up contrasts
specs_exp3 <- pairwise ~ condition | position * part

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp3-stats.RDS")) {
  # Read models from file
  models_exp3 <- readRDS("analysis/export/exp3-stats.RDS")
} else {
  # Compute LMMs for Experiment 3
  models_exp3 <- map(
    comps$name,
    compute_models,
    formula = form_exp3,
    data = data_exp3,
    control = ctrl_params,
    specs = specs_exp3
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/exp3-stats.RDS")
}
```

>>>>

# Do you want to run the analysis for Experiment 3?
run_exp3 <- TRUE

@@

```{r exp3-preproc, eval=run_exp3}
# Read behavioral data for Experiment 1
list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp3

# Update stimulus triggers
preproc_params$event_id <- dict(
  "match/upright" = as.integer(241),
  "match/inverted" = as.integer(242),
  "mismatch/upright" = as.integer(243),
  "mismatch/inverted" = as.integer(244)
)

# Preprocess the EEG for Epxeriment 3 in Python
map2(
  .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp3,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp3

# Backup epochs to the export folder
epochs_exp3$save("analysis/export/exp3-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp3-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp3, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
  write_tsv("analysis/export/exp3-objects.tsv")

# Remove the epochs to free up memory
rm(epochs_exp3)
```

```{r exp3-models, eval=run_exp3}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp3-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    position = factor(position, levels = c("Inverted", "Upright")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions and parts
  filter(condition %in% c("Informed", "Naive") & part != "IV") %>%
  droplevels() -> data_exp3

# Define contrasts for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
contrasts(data_exp3$position) <- MASS::ginv(contrasts_position)
contrasts(data_exp3$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp3$part) <- MASS::ginv(contrasts_part)

# Define new formula for LMMs
form_exp3 <- buildmer::tabulate.formula(
  ~ part * condition * position +
    (part * condition * position | participant) +
    (part * condition * position | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))

# Define new follow-up contrasts
specs_exp3 <- pairwise ~ condition | position * part

# Compute the models for Experiment 3
map(
  comps$name,
  compute_models,
  formula = formula_exp3,
  data = data_exp3,
  control = control,
  specs = specs_exp3
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp3-models.RDS") -> models_exp3
```
